---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# ma206data

<!-- badges: start -->
<!-- badges: end -->

The goal of ma206data is to make the Introduction to Statistical Investigations, Edition II datasets quickly accessible in R.

``` r
remotes::install_github("EvaMaeRey/ma206data")
```

## Here are some datasets made easily available and ready to explore!

```{r example}
library(tidyverse)
library(ma206data)
## basic example code

chap2_Coffee # bam chapter 2 coffee data in your workstation - rock and roll

chap2_Coffee %>% 
  ggplot() +
  aes(cups_per_week) + 
  geom_rug() + 
  geom_histogram() + 
  ggxmean::geom_x_mean() + # development package
  ggxmean::geom_x_mean_label(size = 2) # development package

last_plot() + 
  ggsample::facet_bootstrap(n_facets = 16) # development package

chap10_DraftLottery %>% 
  data.frame() %>% 
  ggplot() + 
  aes(x = sequential_date,
      y = draft_number) + 
  geom_point() + 
  geom_density2d_filled(alpha = .2) + 
  geom_smooth()

last_plot() + 
  ggsample::facet_scramble() # development package
```

# We managed the project by doing the following

## ISI data

- scraping http://www.isi-stats.com/isi2nd/data.html for .txt files, saving them in "isi_txt_data"
- reading those files into r
- saving an .rda file

This was accomplished in "./data-raw/scrape_and_prep_isi_ed2.R".  We quote the code here:

```{r, echo=F}
scrape_and_prep_isi_ed2_script <- readLines("./data-raw/scrape_and_prep_isi_ed2.R")
```

```{r, code = scrape_and_prep_isi_ed2_script, eval = F}

```

## Additional data from course director

- we manually copied in additional data files used in the course into "data-raw/course_director_data"
- read the files into R 
- saved rda files into the data folder

This is accomplished in the script, "./data-raw/prep_course_director_data.R", and the code is shown here:

```{r, echo = F}
prep_course_director_data_script <- readLines("./data-raw/prep_course_director_data.R")
```

```{r, code = prep_course_director_data_script, eval = F}

```


# Documentation

Finally, we coordinated minimal documentation in "./data-raw/write_dataset_minimal_documentation.R"

The code is quoted here:


```{r, echo = F}
write_dataset_minimal_documentation_script <- readLines("./data-raw/write_dataset_minimal_documentation.R")
```

```{r, code = write_dataset_minimal_documentation_script, eval = F}
```
